---
title: "Implementing automated section control sprayers for optimising pesticide application in orchards"
author: "Clemens Stephany, Christoph Weinmann, Lucas Hoffmann, Adrian Fülle, Jasper Hackling"
date: "6/1/2021"
output: html_document
---

\ 

#### Description   
Reducing pesticide use: An analysis on the decision whether to implement an automated or manually operated section control sprayer in orchards.

\ 

#### Decision maker: farmer   
* Farmer is the main stakeholder who makes the decision whether or not to buy a modern sprayer which is able to minimise pesticide application rates

\ 

#### Stake holders: (describe further)
* Farmers 
* Manufacturers 
* Government 
* Consumers 
* Society 
* Food retailers 
* Water suppliers 
* Agrochemical companies 
* NGOs 
* Local biodiversity
* Beekeepers

\ 

#### Problems:    
* Some common agrochemicals will be banned in the near future for various reasons
  + Overuse causes problems 
  + Public opinion is getting worse   
* Excessive use of pesticides can cause unwanted effects (e.g. resistances)  
* Agrochemicals are costly supplies $\Rightarrow$ reduction is welcome  

\ 

#### Options:  
* No change 
* Spray less pesticide with existing machinery 
* Adopt organic farming practices 
* Use beneficiaries (beneficial organisms)
* Spray manually 
* Buy automatic section control sprayer
* Buy manual section control sprayer

\ 

#### Allocation of resources:  
* Money
  + Overheads
  + Running costs 
* Labour 
  + Conducting actual tasks 
  + Acquiring know-how
* Pollinators  

\ 

#### Obstacles:  
* Costs of investment
* Learning curve for running the equipment 
* compatibility with current machinery

#### Uncertainties:  
* Potential reduction of pesticides using an automatic section controlled sprayer
  + Especially the reduction of excessive pesticides
* Common application rates of pesticides in orchards
* Potential Cost of an automatic section controlled sprayer
* Changing climate influencing the frequency of pesticides application
* Increased bee survival rate (as there still are pesticides, just less)
* Added value through increased bee survival and thus increasing pollination
* Governmental interest in pesticides reduction
* Image of a farmer trying to reduce pesticides but still using them
* Maintenance cost of an more complicated and sensitive system

#### (Sources of) information:
* Farmers
  + 
* Manufacturer (Currently developing a prototype)
  + Cost and capabilities of an automatic section control sprayer
* Landwirtschaftskammer NRW
  + Potential subsidisation of automatic section control sprayer
  + Political foreshadowing of future legislations
* (commercial) Beekeepers
  + How much of an problem are pesticides
* Consumers
  + Assess the importance/conception of reduced pesticide application to the consumer 


#### Flow chart using diagrammeR package 
```{r, include=FALSE}
library(DiagrammeR)
library(DiagrammeRsvg)
library(rsvg)
```

<<<<<<< HEAD
```{r, echo=FALSE}
=======
```{r}

>>>>>>> 434aa47af2a00423d747be3049400c4da2a2791f
model_flow_chart <- grViz("
      
digraph boxes_and_circles {

 # Change flow chart orientation (top down: 'TD'; left to right: 'LR' 
 rankdir = 'TD'

 # Add node statements
 node [shape = box
       fontname = Arial
       penwidth = 1, 
       fixedsize = true, 
       width = 3]
       
 # Add edge statements (arrows)
 edge [fontsize = 25
       fontname = Arial]
       
 # Add graph statements 
 graph [nodesep = 0.1]
       
 FP [label = 'Farmers profit']
 M [label = 'Manufacturers']
 Pe [label = 'Pesticides']
 GC [label = 'Government \n concerns']
 FS [label = 'Fruit sales']
 Bio [label = 'Biodiversity']
 Ascs [label = 'Automated section \n controlled sprayer']
 CW [label = 'Contaminated \n water']
 Cu [label = '  Customers']
 
 

 GC->FP [label = ' -',
         fontcolor = 'red',
         color = 'red']
         
 FS->FP [label = '  +',
        fontcolor = 'forestgreen',
        color = 'forestgreen']
 
 Pe->CW [label = '  +',
         fontcolor = 'forestgreen',
         color = 'forestgreen']
 
 CW->GC [label = '  +',
         fontcolor = 'forestgreen',
         color = 'forestgreen']
 
 FP->Ascs [label = '  +',
           fontcolor = 'forestgreen',
           color = 'forestgreen']
 
 Ascs->Pe [label = '  -',
           fontcolor = 'red',
           color = 'red']
           
 M->FP [label = '  -',
        fontcolor = 'red',
        color = 'red']
         
 Bio->FS [label = '  +',
         fontcolor = 'forestgreen',
         color = 'forestgreen']
 
 Pe->Bio [label = '  -',
          fontcolor = 'red',
          color = 'red']
         
 CW->Bio [label = '  -',
          fontcolor = 'red',
          color = 'red']
          
 Pe->Cu [label = '  -',
         fontcolor = 'red',
         color = 'red']
         
 Pe->FS [label = '  +',
         fontcolor = 'forestgreen',
         color = 'forestgreen']
        
 Cu->FS [label = '  +',
         fontcolor = 'forestgreen',
         color = 'forestgreen']
        
 Pe->FP [label = '  -',
         fontcolor = 'red',
         color = 'red']
 
}
")

model_flow_chart
rsvg_png(charToRaw(export_svg(model_flow_chart)), "images/flow-chart.png") 



```



 